Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-08-25 document/ms.tex
actually using more importance samples

\citet{petigura} did not publish or share posterior samples of their
measurements of the physical parameter (\eqalt{samples}).
They did publish a list of periods, radii and radius uncertainties based on
their analysis.
Assuming that there is no measurement uncertainty on the period measurement
and that the radius posterior is Gaussian in linear radius (with a standard
deviation given by the published uncertainty), we draw 256 samples for
$\entry_k$ and use these as an approximation to the posterior probability
function.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.6\textwidth]{figures/smooth/rate.pdf}
\end{center}
\caption{%
{\bf Simulated data}.
The extrapolated rate density of Earth analogs \gammaearth\ as inferred by the
different techniques applied to the \modela\ simulation.
Applying the method used by \citet{petigura} gives a constraint indicated by
the vertical black line with error bars shown as dashed lines.
The histogram is the MCMC estimate of our posterior constraint on this rate
density and the true value is indicated as the thick gray vertical line.
\figlabel{smooth-rate}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.6\textwidth]{figures/simulation/rate.pdf}
\end{center}
\caption{%
{\bf Simulated data}.
The same as \fig{smooth-rate} for \modelb.
\figlabel{simulation-rate}}
\end{figure}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.6\textwidth]{figures/results/rate.pdf}
\end{center}
\caption{%
The extrapolated rate density of Earth analogs \gammaearth\ (the same as
\fig{smooth-rate} but applied to the catalog from \citealt{petigura}).
The histogram is the MCMC estimate of our posterior constraint on this rate
density.
The vertical black line with error bars shown as dashed lines is the result
from \citet{petigura} converted to a rate density by dividing by their bin
volume.
\figlabel{real-rate}}
\end{figure}

>>>>

\citet{petigura} did not publish or share posterior samples of their
measurements of the physical parameter (\eqalt{samples}).
They did publish a list of periods, radii and radius uncertainties based on
their analysis.
Assuming that there is no measurement uncertainty on the period measurement
and that the radius posterior is Gaussian in linear radius (with a standard
deviation given by the published uncertainty), we draw 512 samples for
$\entry_k$ and use these as an approximation to the posterior probability
function.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/smooth/rate.pdf}
\end{center}
\caption{%
{\bf Simulated data}.
The extrapolated rate density of Earth analogs \gammaearth\ as inferred by the
different techniques applied to the \modela\ simulation.
Applying the method used by \citet{petigura} gives a constraint indicated by
the vertical black line with error bars shown as dashed lines.
The histogram is the MCMC estimate of our posterior constraint on this rate
density and the true value is indicated as the thick gray vertical line.
\figlabel{smooth-rate}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/simulation/rate.pdf}
\end{center}
\caption{%
{\bf Simulated data}.
The same as \fig{smooth-rate} for \modelb.
\figlabel{simulation-rate}}
\end{figure}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/results/rate.pdf}
\end{center}
\caption{%
The extrapolated rate density of Earth analogs \gammaearth\ (the same as
\fig{smooth-rate} but applied to the catalog from \citealt{petigura}).
The histogram is the MCMC estimate of our posterior constraint on this rate
density.
The vertical black line with error bars shown as dashed lines is the result
from \citet{petigura} converted to a rate density by dividing by their bin
volume.
\figlabel{real-rate}}
\end{figure}
